# API

## Exercise 1

Using the Github or similar API, find an endpoint in the documentation that
doesn't require authentication and use Postman to run 2-3 simple GET queries.

## Exercise 2

Find and signup to an API service, this could be one listed in the slides or
any other API you can find. Take a look at the documentation and see if you
can authenticate via Oauth using the example R code provided in the slides and
the documentation for the `httr` package.

You can access the documentation by running `?httr` from any R console.

If the API you find doesn't require authentication, try running a simple
GET query using `httr`. I you aren't sure, mock the query first using
postman.

### Example GET request

```{r}
library(httr)

response <- httr::GET("https://api.github.com/users/raymanns/starred")

status_code(response)

# headers(response)

data <- content(response)

for (value in data[0:5]) {
    print(value$name)
}
```

### Example OAuth 2.0 using client credentials

```{r}
library(httr)

# Get secrets, set this in ~/.Renviron file
clientID <- Sys.getenv("SPOTIFY_CLIENT_ID")
clientSecret <- Sys.getenv("SPOTIFY_CLIENT_SECRET")

# OAuth is a common authentication strategy
myapp <- httr::oauth_app("test", clientID, clientSecret)
authEndpoint <-
    httr::oauth_endpoint(authorize = "https://accounts.spotify.com/authorize",
                         access = "https://accounts.spotify.com/api/token")

r <- httr::oauth2.0_access_token(authEndpoint, 
                                 myapp,
                                 code = NULL,
                                 use_basic_auth = TRUE, 
                                 client_credentials = TRUE)

accessToken <- r$access_token
print(accessToken)
```

### Example GET request with query string

```{r}
library(httr)

# Search
searchEndpoint <- "https://api.spotify.com/v1/search"

search <- httr::GET(searchEndpoint,
                    query = list(q="Muse",
                                 type="artist,track",
                                 limit=5),
                    encode = "json",
                    httr::add_headers(Authorization = paste("Bearer",
                                                            accessToken)))

print(search$request$url)

results <- content(search, "parsed", encoding = "UTF-8")

for (item in results$artists$items) {
    print(paste(item$name, "-", item$followers$total))
}
```

